Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-14 paper/section_2_literature.tex
Add LSTM + weighted RoBERTa results

BPE offers an elegant solution to handling an open vocabulary. To date the only
image captioning work that uses BPE is~\cite{Sharma2018ConceptualCA}, but they
did not use it for rare named entities as these were removed from
the captions during pre-processing. In contrast we explicitly examine the use
of BPE for generating rare names and evaluate it in comparison to
template-based methods.

>>>>

BPE offers an elegant solution to handling an open vocabulary. To date the only
image captioning work that uses BPE is~\cite{Zhao2019InformativeIC}, but they
did not use it for rare named entities as these were removed from
the captions during pre-processing. In contrast we explicitly examine the use
of BPE for generating rare names and evaluate it in comparison to
template-based methods.
